---
title: 'Reproducibility Assignment: Question 4'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### a) Set working directory and load the necessary packages

The working directory will be different for every user. 
Set the directory to where the "penguins-main" folder is saved on your computer. 
```{r}
#setwd("insert file path here")

#This file contains the libraries needed to carry out this analysis. Check that all libraries are installed already.
source("functions/libraries.r") 
```



### b) Load and appropriately clean the data 
To make the penguin data easier to analyse, we should tidy it up using our saved cleaning functions.
```{r}
#First we need to load our raw data
penguins_raw <- read.csv("data_raw/penguins_raw.csv")
head(penguins_raw) #This shows us the first 6 rows of our raw dataset.

#Next we need to load the cleaning functions
source("functions/cleaning.r")  
penguins_clean <- cleaning(penguins_raw) #This function ensures all our column headings are in the same format, removes empty rows and columns, and removes certain columns
head(penguins_clean) #This shows us the first 6 rows of our clean dataset

penguins_culmen <- remove_empty_culmen_depth(penguins_clean) #This function removes any columns that are irrelevant to our analysis, and takes out any rows containing NA for our variables of interest. 
penguins_culmen #This shows us what is remaining in our dataset


```

### c) Run a statistical test on the Palmer Penguins dataset
I want to determine the effect of penguin species, body mass, and their interaction on penguin culmen depth. To do this I will create a linear model and run an ANCOVA test.

```{r}

lm_culmen_depth <- lm(culmen_depth_mm ~ body_mass_g*species, penguins_culmen)
summary(lm_culmen_depth)
  anova(lm_culmen_depth)
```

This ANCOVA revealed there is no statistically significant interaction between body mass and species (F(2, 336)= 0.7377, p=0.479). This means culmen depth does not have a different relationship with body mass in different penguin species.  
However, the ANCOVA also revealed that there is a statistically significant main effect of body mass (F(1,336)=382.9, p<0.0001) and of species (F(2,336)=499.5, p<0.0001). 

The R-squared value tells us that our main effects of body mass and species explain approximately 80% of the variation in culmen depth.

We can explore the effect of body mass and species on culmen depth further by visualising the data. 


### d) Produce a figure that explains the statistical test
```{r, out.width = "150%"}

#To make the figure we are going to use a function I made earlier.
source("functions/plotting.r") #Load the plotting function
culmen_scatterplot <- plot_culmen_figure(penguins_culmen) #This plots the figure
culmen_scatterplot



```
This scatterplot supports that there is no significant interaction between penguin species and body mass because the regression lines have a vary similar gradient.   
The steep gradient of each regression line shows the main effect of body mass; as body mass increases, so does culmen depth.  
Finally, whilst Adelie and Chinstrap penguins have similar culmen depths, the culmens of Gentoo penguins are shallower. 

### e) Save the plot
We can save the plot using saving functions.

```{r}
source("functions/saving.r") #import the saving functions
save_culmen_plot_png(penguins_culmen, "figures/culmen_scatterplot.png", width= 10, height= 7, res=600, scaling =0.5) #This function saves the plot as a png

save_culmen_plot_svg(penguins_culmen, "figures/culmen_scatterplot.svg", width=10, height=7, scaling =1) #This function saves the plot as an svg

```







